Suitability prevalence area index in late quaternary explains genetic diversity in Tassel eared Squirrels

### 2023-07-08 manuscript_english.Rmd
Adding word document

---
title: "Suitability prevalence area index in late quaternary explains genetic"
author: "Norma Hernandez, Angel Robles, Nathan Upham"
date: "2023-07-08"
output: word_document
bibliography: R21_citation.bib
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

## Discussion

>>>>

---
title: Suitability prevalence area index in late quaternary explains genetic diversity in Tassel eared Squirrels
author: "Norma Hernandez, Angel Robles Nathan Upham"
date: "2023-06-27"
includes:
  in_header: preamble.tex
output: 
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex 
    keep_tex: true
bibliography: R21_citation.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@
